---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

 [![CRAN status](https://www.r-pkg.org/badges/version/stdsim)](https://cran.r-project.org/package=stdsim)
 [![DOI](https://zenodo.org/badge/204009603.svg)](https://zenodo.org/badge/latestdoi/204009603)

# stdsim

The goal of stdsim is to simulate sample and standard measurements to allow optimisation of the Empirical Transfer Function, the calibration from the machine scale of standards to an absolute reference frame.

## Installation

You can install the released version of stdsim from [GitHub](https://github.com/japhir) with:

``` r
devtools::install_github("japhir/stdsim")
```

## Example

This shows how to run one simulation with some input parameters:

```{r example}
options(genplot=TRUE, verbose=TRUE)
library(stdsim)
sim_stds(stdfreqs=c(1, 1, 9, 0, 0), stdn=50, smpn=30, stdev=25, smpt=5, out="pl")
```

# Citation

When you use this software, please also cite the article for which this R package was written:

Kocken, I. J., Müller, I. A., & Ziegler, M. (2019). Optimizing the use of carbonate standards to minimize uncertainties in clumped isotope data. Geochemistry, Geophysics, Geosystems, 20(11), 5565–5577. https://doi.org/10.1029/2019GC008545
